\chameleon{}: Untangling Type Errors Through Interactive Visualization and Exploration

### 2022-11-23 sections/evaluation.tex
Fix latex errors

\begin{figure}[h]
    \centering
    \Description{A timeline of \chameleon{} evaluations}
    \includegraphics[width=\linewidth]{images/timeline.pdf}
    \caption{The timeline of \chameleon{}  development and 
    evaluation.}
    \label{fig:timeline}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \Description{Chameleon v1}
    \includegraphics[width=\linewidth]{images/chameleon-v1.pdf}
    \caption{
        \chameleon{} Version 1
        }
    \label{fig:chameleon-v1}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \Description{Time to complete by task in user study 1 with confidence interval}
    \includegraphics[width=\linewidth]{images/r1-data.pdf}
    \caption{Time to complete by task in user study 1 with confidence interval}
    \label{fig:r1-analysis}
\end{figure}

\begin{figure}[h]
    \centering
    \Description{Time to complete by task in user study 2 confidence interval}
    \includegraphics[width=\linewidth]{images/r2-data.pdf}
    \caption{Time to complete by task in user study 2 confidence interval}
    \label{fig:r2-analysis}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \Description{
    Time to complete by task in user study 2 with confidence interval}
    \includegraphics[width=\linewidth]{images/r4-analysis.pdf}
    \caption{Time to complete by task in user study 4 with confidence interval}
    \label{fig:r4-analysis}
\end{figure}

\begin{figure}[h]
    \centering
    \Description{a screenshot from user study for version 2}
    \includegraphics[width=\linewidth]{images/r4-task9.png}
    \caption{
High interaction users were able to locate the exact line for a potential fix after navigating to deduction step 6 or 7, which directly revealed the true cause of the type error. After this, 12 out of 15 high interaction users provided the most ideal fix in the first try. Low interaction group  takes longer time to examine the problem, provided wrong fixes in the initial trials. One participant fixed a minor run-time issue (a problematic pattern matching of `[attributes]` on line 18) however failed to identify the culprit of the type error.
    }
    \label{fig:r4-task9}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/r4-mode-switching.png}
    \caption{
        \textbf{Row Number of tasks }

    }
    \label{fig:r4-mode-switching}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/timeline.pdf}
    \caption{The timeline of \chameleon{}  development and 
    evaluation.}
    \label{fig:timeline}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/chameleon-v1.pdf}
    \caption{
        \chameleon{} Version 1
        }
    \label{fig:chameleon-v1}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/r1-data.pdf}
    \caption{Time to complete by task in user study 1 with confidence interval}
    \label{fig:r1-analysis}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/r2-data.pdf}
    \caption{Time to complete by task in user study 2 confidence interval}
    \label{fig:r2-analysis}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/r4-analysis.pdf}
    \caption{Time to complete by task in user study 4 with confidence interval}
    \label{fig:r4-analysis}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/r4-task9.png}
    \caption{
High interaction users were able to locate the exact line for a potential fix after navigating to deduction step 6 or 7, which directly revealed the true cause of the type error. After this, 12 out of 15 high interaction users provided the most ideal fix in the first try. Low interaction group  takes longer time to examine the problem, provided wrong fixes in the initial trials. One participant fixed a minor run-time issue (a problematic pattern matching of `[attributes]` on line 18) however failed to identify the culprit of the type error.
    }
    \label{fig:r4-task9}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{images/r4-mode-switching.png}
    \caption{
        The rows represent the finishing mode, columns starting modes.
    }
    \label{fig:r4-mode-switching}
\end{figure}
